Git Learning Notes

### 2015-01-10 ch-wox/ch-wox.tex
After first review in 2014

Metallic tungsten powders were utilized as source materials in this work. Four kinds of W powder were used in total, as summarized in Table~\ref{tab:powder}. Two growth configurations were explored, namely ordinary transport and seeded growth.
% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{Tungsten powders size and purity}\label{tab:powder}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Results ans Discussion}
\subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}

@@

% nawox sem edx
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires. (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
\label{fig:nawoxsemedx}
\end{figure}

@@

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{cccc}
\toprule
Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}
For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate is shown in Table.~\ref{tab:woram2}. 
\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & 263(w), 272(w), 311(w), 366(w), 777(vs), 794(s), 949(m) &\cite{Fomichev1992}\\
\ce{Na5W14O44} & 107(s),695(m), 765(vs), 913(w), 943(m), 965(m)& this work\\
\bottomrule
\end{tabular}

@@

A mechanism of residue deposition enhanced growth was proposed to explain the morphology evolution of the nanowires with the growth number. Since the CVD setup employed in this thesis is a hot-wall system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area. Residue deposition was found on the quartz tube which can be distinguished by the color change on the quartz tube after each growth. With the increase of growth number for the same reaction chamber, the residue deposition on the inner wall of the tube also increased. If a clean quartz tube free of any residue deposition is used as the reaction chamber, the vapors are supplied only from the source material forming deposition in the growth area with lower temperature (as shown by the schematics in Fig.~\ref{fig:nawoxsch}a). When a quartz tube with residue deposition from previous depositions is used repeatedly as the reaction chamber, the residue deposition heated at growth temperature will also produce vapor locally. Therefore, the vapors from both the source materials and the local residue deposition will result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b). To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g. a growth number of 9). The experiments were carried out without any source materials while other growth parameters remain the same. Similar nanowires were found on the substrate in the nanowire growth zones. Without the source materials, the residue deposition from the tube surface was the only possible source that could produce vapors forming nanowires on the substrate (Fig.~\ref{fig:nawoxsch}c). This result confirmed the nanowire growth could be enhanced by the presence of the residue deposition and explained the morphology changes of the nanowires with the increase of growth number.
% xrd na5
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{wox_xrd_series}
\caption{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
\label{fig:nawoxxrd}
\end{figure}

The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition. The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition. Fig.~\ref{fig:nawoxxrd} displays the XRD spectra of a series of specimens with the growth number increases from 1 to 5. The XRD spectra reveal the relative concentration dynamics of the three phases as the growth number increases. Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5. And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases. These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b). Details XRD indices assignment is summarized in Table~\ref{tbl:wo3xrd}.

\begin{table}
\centering
\caption{XRD assignments of specimens in \ce{Na_xWO3} growth}\label{tbl:wo3xrd}
\begin{tabular}{llllll}
\toprule
\ce{WO3} &          &\ce{Na5W14O44} &      & \ce{Na2W4O13} & \\
2$\theta$   & hkl   & 2$\theta$   & hkl    & 2$\theta$   & hkl   \\
\midrule
 23.05   & 0 0 2 & 9.65    & 0 0 2  & 10.85   & 1 0 0 \\
 23.59   & 0 2 0 & 14.49   & 0 0 3  & 21.8    & 2 0 0 \\
 24.31   & 2 0 0 & 19.37   & 0 0 4  & 32.97   & 3 0 0 \\
 26.60   & 1 2 0 & 24.27   & 0 0 5  & 56.45   & 5 0 0 \\
 34.10   & 2 0 2 & 29.22   & 0 0 6  &         &       \\
 47.11   & 0 0 4 & 39.36   & 0 0 8  &         &        \\
 48.29   & 0 4 0 & 44.46   & 0 0 9  &         &        \\
 49.79   & 4 0 0 & 49.71   & 0 0 10 &         &        \\
         &       & 55.23   & 0 0 11 &         &        \\
         &       & 60.77   & 0 0 12 &         &        \\
\bottomrule
\end{tabular}
\end{table}

@@

The optical transmission and reflection properties of the as-grown \ce{Na5W14O44} NWs were evaluated using UV-Vis spectroscopy, as shown in Fig.~\ref{fig:ch3naxuvvis}. The sample was prepared on a quartz substrate, which is transparent from 300 to 1300 nm. SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect is not sensitive to the substrate. 
%051412 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:nauv}\includegraphics[width=0.45\textwidth]{uvvis_naxwo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
\caption[UV-Vis and \gls{drs} of \ce{Na5W14O44} NWs on quartz]{UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz: (a) Optical transmission and (b) diffuse reflection spectra.}
\label{fig:ch3naxuvvis}
\end{figure}
The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength. This variation was also identified in the diffuse reflection spectrum in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm. One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm. The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting an energy gap edge at about 380 nm. This is consistent with the observed white sample color; however, the conductivity of \ce{Na5W14O44} has not been investigated experimentally. Based on the electron sum rule, the sodium tungsten oxide can be cast into \ce{Na5W_1^{5+}W_{13}^{6+}O44}, which indicates the W atom state is quite close to that in \ce{WO3}. More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW.

\subsubsection{Ordinary transport growth using other W powders}
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}

@@

As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produces thin film deposition, and growth using 3N powder is plagued with the impurity effect producing sodium tungsten oxide NW instead of tungsten oxide NW. New growth method is thus explored to obtain \ce{WO3} NWs. In this study, a seeded growth approach was developed and proved to be a successful alternative way. In the seeded growth, additional tungsten powders was used on the substrate serving as local seed, on which dense \ce{WO3} NW array grew.

@@

With all above oxidation experiments, favorable conditions for local growth of NWs were extracted to perform seeded growth. The seeded growth was performed by placing high purity tungsten powders (4N5 or 5N) in heating zone and receiving substrate with 3N tungsten powders in downstream location where the temperature was about 600 \si{\degreeCelsius}. The temperature profile and source and substrate locations remain essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on substrate. In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates and the growth time was kept at 4 h.
% sg sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
\caption[SEM characterization of \ce{WO3}seeded growth]{SEM characterization of \ce{WO3}seeded growth. (a) SEM graphs of \ce{WO3} NWs on \ce{SiO2}/Si substrate. (b) A high magnification view showing uniform NW growth and close-up view of one NW.}
\label{fig:woseedsem}
\end{figure}
As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 10 $\mu$m and diameter about 50 to 200 nm, according to the measurements made in the close-up view. Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions. It was occasionally observed that NWs growth was initiated adjacent some tungsten powders. This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders. It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases. This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply. Similar phenomena were observed in other studies. \citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}

@@

\subsection{Tungsten Oxides: Misc}

>>>>

Metallic tungsten powders were utilized as source materials in this work. Four kinds of W powder were used in total, as summarized in Table~\ref{tab:powder}. Two growth configurations were explored, namely ordinary transport and seeded growth.
% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{Tungsten powder sizes and purities}\label{tab:powder}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Results and Discussion on 1D Nanowire Growth}
\subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}

@@

% nawox sem edx
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_semedx.jpg}
\caption[SEM and EDX on \ce{Na_xWO3}]{SEM images of (a) dense array of the as-synthesized ultra-long nanowires on \ce{SiO2}-Si substrate and (b) rectangular microplates grow among the nanowires. (c) EDS and (d) XRD spectra showing the chemical compositions and phases of the deposition.}
\label{fig:nawoxsemedx}
\end{figure}

@@

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{cccc}
\toprule
Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}
For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate is shown in Table.~\ref{tab:woram2}. 
\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten oxides}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & 263(w), 272(w), 311(w), 366(w), 777(vs), 794(s), 949(m) &\cite{Fomichev1992}\\
\ce{Na5W14O44} & 107(s),695(m), 765(vs), 913(w), 943(m), 965(m)& this work\\
\bottomrule
\end{tabular}

@@

A mechanism of residue deposition enhanced growth was proposed to explain the morphology evolution of the nanowires with the growth number. Since the CVD setup employed in this thesis is a hot-wall system, deposition formed on the substrate surface as well as on the inner wall of the reaction chamber in the growth area. Residue deposition was found on the quartz tube which can be distinguished by the color change on the quartz tube after each growth. With the increase of growth number for the same reaction chamber, the residue deposition on the inner wall of the tube also increased. If a clean quartz tube free of any residue deposition is used as the reaction chamber, the vapors are supplied only from the source material forming deposition in the growth area with lower temperature (as shown by the schematics in Fig.~\ref{fig:nawoxsch}a). When a quartz tube with residue deposition from previous depositions is used repeatedly as the reaction chamber, the residue deposition heated at growth temperature will also produce vapor locally. Therefore, the vapors from both the source materials and the local residue deposition will result in an enhanced growth of nanowires (Fig.~\ref{fig:nawoxsch}b). To prove this hypothesis, control experiments were performed utilizing a quartz tube used multiple times previously (e.g. a growth number of 9). The experiments were carried out without any source materials while other growth parameters remain the same. Similar nanowires were found on the substrate in the nanowire growth zones. Without the source materials, the residue deposition from the tube surface was the only possible source that could produce vapors forming nanowires on the substrate (Fig.~\ref{fig:nawoxsch}c). This result confirmed the nanowire growth could be enhanced by the presence of the residue deposition and explained the morphology changes of the nanowires with the increase of growth number.
%xrd na5
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{wox_xrd_series}
\caption[XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5]{XRD spectra of the as-synthesized specimen with the increase of growth number from 1 to 5.}
\label{fig:nawoxxrd}
\end{figure}
The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition. The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition. Fig.~\ref{fig:nawoxxrd} displays the XRD spectra of a series of specimens with the growth number increases from 1 to 5. The XRD spectra reveal the relative concentration dynamics of the three phases as the growth number increases. Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5. And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases. These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b). Details XRD indices assignment is summarized in Table~\ref{tbl:wo3xrd}.

\begin{table}
\centering
\caption{Assignment of XRD peak indices to different phases}\label{tbl:wo3xrd}
\begin{tabular}{llllll}
\toprule
\ce{WO3} &          &\ce{Na5W14O44} &      & \ce{Na2W4O13} & \\
2$\theta$   & hkl   & 2$\theta$   & hkl    & 2$\theta$   & hkl   \\
\midrule
 23.05   & 0 0 2 & 9.65    & 0 0 2  & 10.85   & 1 0 0 \\
 23.59   & 0 2 0 & 14.49   & 0 0 3  & 21.8    & 2 0 0 \\
 24.31   & 2 0 0 & 19.37   & 0 0 4  & 32.97   & 3 0 0 \\
 26.60   & 1 2 0 & 24.27   & 0 0 5  & 56.45   & 5 0 0 \\
 34.10   & 2 0 2 & 29.22   & 0 0 6  &         &       \\
 47.11   & 0 0 4 & 39.36   & 0 0 8  &         &        \\
 48.29   & 0 4 0 & 44.46   & 0 0 9  &         &        \\
 49.79   & 4 0 0 & 49.71   & 0 0 10 &         &        \\
         &       & 55.23   & 0 0 11 &         &        \\
         &       & 60.77   & 0 0 12 &         &        \\
\bottomrule
\end{tabular}
\end{table}

@@

The optical transmission and reflection properties of the as-grown \ce{Na5W14O44} NWs were evaluated using UV-Vis spectroscopy, as shown in Fig.~\ref{fig:ch3naxuvvis}. The sample was prepared on a quartz substrate, which is transparent from 300 to 1300 nm. SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect is not sensitive to the substrate. 
%051412 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:nauv}\includegraphics[width=0.45\textwidth]{uvvis_naxwo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
\caption[UV-Vis and \gls{drs} of \ce{Na5W14O44} NWs on quartz]{UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz: (a) Optical transmission and (b) diffuse reflection spectra.}
\label{fig:ch3naxuvvis}
\end{figure}
The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength. This variation was also identified in the diffuse reflection spectrum in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm. One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm. The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting an energy gap edge at about 380 nm. This is consistent with the observed white sample color; however, the conductivity of \ce{Na5W14O44} has not been investigated experimentally. Based on the electron sum rule, the sodium tungsten oxide can be cast into \ce{Na5W_1^{5+}W_{13}^{6+}O44}, which indicates the W atom state is quite close to that in \ce{WO3}. More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NWs.

\subsubsection{Ordinary transport growth using other W powders}
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature, (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}

@@

As mentioned in Sec.~\ref{sec:nawox}, growth using higher purity tungsten powders primarily produces thin film deposition, and growth using 3N powder is plagued with the impurity effect producing sodium tungsten oxide NW instead of tungsten oxide NW. New growth method was thus explored to obtain \ce{WO3} NWs. In this study, a seeded growth approach was developed and proved to be a successful alternative way. In the seeded growth, additional tungsten powders was used on the substrate serving as local seed, on which dense \ce{WO3} NW array grew.

@@

With all above oxidation experiments, favorable conditions for local growth of NWs were extracted to perform seeded growth. The seeded growth was performed by placing high purity tungsten powders (4N5 or 5N) in heating zone and receiving substrate with 3N tungsten powders in downstream location where the temperature was about 600 \si{\degreeCelsius}. The temperature profile and source and substrate locations remain essentially the same as in Fig.~\ref{fig:wogrow} except the presence of 3N powder on substrate. In all experiments, tungsten powders were uniformly distributed by sliding two pieces of substrates and the growth time was kept at 4 h.
% sg sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:sga}\includegraphics[width=0.4\textwidth]{wox_sg_a.jpg}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:sgb}\includegraphics[width=0.4\textwidth]{wox_sg_b.jpg}}
\caption[SEM characterization of \ce{WO3} seeded growth]{SEM characterization of \ce{WO3} seeded growth. (a) SEM graphs of \ce{WO3} NWs on \ce{SiO2}/Si substrate. (b) A high magnification view showing uniform NW growth and close-up view of one NW.}
\label{fig:woseedsem}
\end{figure}
As shown in Fig.~\ref{fig:sgb}, dense NWs array was obtained on tungsten powder seeds with individual wires of length up to 10 $\mu$m and diameter about 50 to 200 nm, according to the measurements made in the close-up view. Each tungsten powder stood as independent growth site (Fig.~\ref{fig:sga}) with island-layer growth on the substrates, a common feature without using tungsten powder as seed under current experimental conditions. It was occasionally observed that NWs growth was initiated adjacent some tungsten powders. This phenomenon was correlated to the local trap of vapor flow since it was more often found among the enclosed area by tungsten powders. It is also found that the diameter of NWs decrease as the distance between powders and upstream edge increases. This is a combination effect of lower temperature and reduced \ce{WOx} growth species supply. Similar phenomena were observed in other studies. \citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}

@@

\subsection{Tungsten Oxides: Other Methods}
